Clicks and Cliques

### 2017-10-09 papersoul.Rnw
replace _each() by _at()

<<data2,cache=TRUE, echo=FALSE,warning=FALSE,message=FALSE,eval=FALSE>>=
# Data contain on 'sotc.csv' file were pre-processed by Xiaoque Cheng with mergeGUI. 
soul <- read.csv('data/sotc.csv', header=T)

@@

map <- get_map(location = 'united states', zoom = 4, maptype = "terrain", source = "google")

@@

p <- ggmap(map, extent = "device")
p + geom_point(data = aux.mer, mapping = aes(lon, lat), size = 6*aux.mer$cate, alpha = .4) + xlab('') + ylab('') + theme(axis.text.x = element_blank(), axis.text.y = element_blank()) 
@
  \caption{Location of the 26 communities analyzed, size of dot represent population. Only two communities on the west coast. \label{map}}
\end{figure}

@@

#dat.aux <- melt(data=census.data,id.vars='QSB',measure.vars=c("Less.than.high.school.graduate.","High.school.graduate.","Some.college.or.associate.s.degree.","Bachelor.s.degree.or.higher.") ) 
#or.aux <- rep(dat.aux$value[dat.aux$variable=="Bachelor.s.degree.or.higher."],4)
#dat.aux$QSB <- with(dat.aux, reorder(x=QSB, X=or.aux  ) )

@@

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=

# att.rf <- randomForest(Not.Attached ~ . , data=census.data[,c(2:63,66)], importance=T, ntree=2000)
# aux <- dat.cor[order(dat.cor$cor), ]
# aux <- subset(aux, type=='Attached')
# var.cl1 <- as.character(aux$vars[c(1:10,51:61)])
# d <- dist(census.data[, var.cl1])
# hc <- hclust(d, method='average')
# census.data$cl.att <- cutree(hc,3)
# var.cl2 <- colnames(census.data)[c(3,8,12,17,21,22,28,31,48)]

var.cl2 <- colnames(census.data) %in% c("aveageF","prop1821", "Bachelor.s.degree.or.higher." , "gini" , "own.rate" , "afri.prop",'prop.new.entry','un.rate',"prop.no.workers" )
d2 <- dist(census.data[, var.cl2])
hc2 <- hclust(d2, method = 'ward.D')
census.data$cl.2 <- cutree(hc2,4)

# Characterize the clusters with the numerical variables
#aux <- split(census.data[,c(3,8,12,17,21,22,28,31,48)], census.data$cl.2)
aux <- split(census.data[, var.cl2], census.data$cl.2)
aux1 <- ldply(aux, function(x) apply(x, 2, mean) )
colnames(aux1) <- c('cl.2', 'Age.Fem', '1821.Yr','Bachelor', 'Unemp','Gini','Own.rate', 'Afri.pr', 'No.workers', 'New.entry' )

#aux1$cl.id <- as.factor(aux1$cl.2)
ggparcoord(aux1[,-11], columns = -1, scale = 'std', groupColumn = 'cl.2', showPoints = T, order = c(3, 4, 6, 10, 2, 5, 9, 7, 8))  + theme(axis.text.x = element_text(angle = 90, size = I(15))) + xlab('') + ylab('') + scale_color_brewer(type = 'qual', palette = 2, name = 'Group')
@
\caption{Parallel coordinate plot for community cluster means \label{cluster.cen}.  }
\end{figure}

>>>>

<<data2, cache=TRUE,echo=FALSE,warning=FALSE,message=FALSE,eval=FALSE>>=
# Data contain on 'sotc.csv' file were pre-processed by Xiaoque Cheng with mergeGUI.
soul <- read.csv('data/sotc.csv', header=T)

@@

mapp <- get_googlemap(location = 'united states', zoom = 4, maptype = "terrain")

@@

p <- ggmap(mapp, extent = "device")
p + geom_point(data = aux.mer, mapping = aes(lon, lat), size = 6*aux.mer$cate, alpha = .4) + xlab('') + ylab('') + theme(axis.text.x = element_blank(), axis.text.y = element_blank())
@
  \caption{Location of the 26 communities analyzed, size of dot represent population. Only two communities on the west coast. \label{map}}
\end{figure}

@@

@@

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=
var.cl2 <- colnames(census.data) %in% c("aveageF","prop1821", "Bachelor.s.degree.or.higher." , "gini" , "own.rate" , "afri.prop",'prop.new.entry','un.rate',"prop.no.workers" )
d2 <- dist(census.data[, var.cl2])
hc2 <- hclust(d2, method = 'ward.D')
census.data$cl.2 <- cutree(hc2,4)

# Characterize the clusters with the numerical variables
nn <- c('cl.2', 'Age.Fem', '1821.Yr','Bachelor', 'Unemp','Gini','Own.rate', 'Afri.pr', 'No.workers', 'New.entry' )

census.data %>% select( c(colnames(census.data)[var.cl2],'cl.2' ) ) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  setNames(nn) %>% ungroup() %>%
  mutate(cl.2 = factor(cl.2)) %>%
  ggparcoord(columns = 2:10, scale = 'std', 
             groupColumn = 'cl.2', showPoints = T, 
             order = c(3, 4, 6, 10, 2, 5, 9, 7, 8))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  xlab('') + ylab('') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')
@
\caption{Parallel coordinate plot for community cluster means \label{cluster.cen}.  }
\end{figure}
